### 2024-03-01 supporting.tex
Added contrasts figure to supporting.tex

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{contrasts/out/contrasts.png}
\centering
\caption{\textbf{Sample contrasts calculation.}
\textbf{(A)} Initial state of tree with three tips. Values of traits at each tip are indicated on the tree and in the table.
\textbf{(B)} Calculation of first contrast between tips B and C.
\textbf{(C)} Inference of trait value at internal node A. Its branch length is increased to account for the uncertainty in the estimation of its value.
\textbf{(D)} Calculation of second contrast between tip D and internal node A.}
\label{sfig:contrasts}
\end{figure}
